An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
brief pass

It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
Suppose we have the feature space $\X$ and label space $\Y$.
%For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
A surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $\D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $h_1,h_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence the linked hypotheses limits to the optimal target loss $\ell^*$.

\begin{definition}\label{def:consistency}
	Given a loss $L : \reals^d \to \reals^\Y_+$ and link $\psi : \reals^d \to \R$, the pair $(L, \psi)$ is \emph{consistent} with respect to a target loss $\ell : \R \to \reals^\Y_+$ if, for all $\D \in \Delta(X \times \Y)$ and all sequences of measurable functions $\{h_m : \X \to \reals\}$, we have
	\begin{align*}
		\E_{(X,Y) \sim \D} L(h_m(X), Y) \to \inf_h  \E_{(X,Y) \sim \D} L(h(X), Y) &\implies \E_{(X,Y) \sim \D} \ell(\psi \circ h_m(X), Y) \to \inf_f  \E_{(X,Y) \sim \D} \ell(\psi \circ h(X), Y)~.
	\end{align*}
\end{definition}

When the hypothesis class $\H$ is not the set of all measurable functions and Definition~\ref{def:consistency} is updated accordingly, calibration and consistency are not equivalent~\citep{long2013consistency,kuznetov2014multiclass,zhang2020convex}.
See \S~\ref{sec:conclusion} for further discussion about extending our results to this setting.
\jessiet{Not sure if we want this paragraph... at least here?}

@@

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
For example, the min-max objective in the literature on adversarial prediction~\citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial,fathony2018consistent} is a special case of this construction when one unfolds the definition of the convex conjugate of $-\risk \ell$.
% reducing to  playing the role of their is a maximum of affine functions, and the conjugate takes the infimum (which is always attained) so $C = (-\risk \ell)^*$ used in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} lines up with their min-max objective.  
%\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?  We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}
%\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, which excludes polyhedral surrogates.
Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general}\jessiet{Does this citation need to be updated?}.

@@

To do so, given $u \in U_\epsilon \cap U'_\epsilon \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U_\epsilon,U'_\epsilon$, etc.
The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one permitted value for $\psi(u)$ remains.
This claim follows from a geometric result (Lemma~\ref{lem:thick-intersect}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
When they do intersect, eq.~\eqref{eq:intersection-property-embedding} implies that there exists a permitted choice of link for the intersection of the thickenings.
It is crucial that, by Lemma~\ref{lem:polyhedral-range-gamma}, polyhedral surrogates only have finitely many sets of the form $U = \Gamma(p)$.
Together, these observations yield a single uniform smallest\jessiet{largest?} $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
%Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.

@@

\mytodo{gray!20!white}{Cover: A}
Finally, a third proof of Theorem~\ref{thm:poly-ie-implies-consistent} is implicit in \citet[Theorem 8]{ramaswamy2016convex}.
The authors use an entirely different link construction involving the superprediction set of the surrogate loss.
We discuss their result and how it relates to our work in \S~\ref{app:ccdim-construction}.

@@

\paragraph{Polyhedral vs.\ smooth surrogates}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
\reviewertwo{B}
\footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the full conditional label distributions, can improve performance in limited data settings.
We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
  % See references recommended by Peter Bartlett.}
%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.

>>>>

It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, as defined next (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
Let feature space $\X$ and label space $\Y$ be given.
%For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Intuitively, a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $\D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $h_1,h_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence the linked hypotheses limits to the optimal target loss $\ell^*$.

\begin{definition}\label{def:consistency}
	Given a loss $L : \reals^d \to \reals^\Y_+$ and link $\psi : \reals^d \to \R$, the pair $(L, \psi)$ is \emph{consistent} with respect to a target loss $\ell : \R \to \reals^\Y_+$ if, for all $\D \in \Delta(X \times \Y)$ and all sequences of measurable functions $\{h_m : \X \to \reals\}$, we have
	\begin{align*}
		&\E_{(X,Y) \sim \D} L(h_m(X), Y) \to \inf_h  \E_{(X,Y) \sim \D} L(h(X), Y)
    \\
    &\implies \;\; \E_{(X,Y) \sim \D} \ell(\psi \circ h_m(X), Y) \to \inf_f  \E_{(X,Y) \sim \D} \ell(\psi \circ h(X), Y)~.
	\end{align*}
\end{definition}

When working with a restricted hypothesis class $\H$, as opposed to the set of all measurable functions in Definition~\ref{def:consistency}, then the corresponding notion of consistency (called \emph{$\H$-consistency}) is no longer equivalent to calibration~\citep{long2013consistency,kuznetov2014multiclass,zhang2020convex};
see \S~\ref{sec:conclusion} for further discussion.

@@

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
For example, the min-max objective in the literature on adversarial prediction~\citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial,fathony2018consistent} is a special case of this construction when one unfolds the definition of the convex conjugate of $-\risk \ell$.
% reducing to  playing the role of their is a maximum of affine functions, and the conjugate takes the infimum (which is always attained) so $C = (-\risk \ell)^*$ used in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} lines up with their min-max objective.  
%\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?  We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}
%\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, which excludes polyhedral surrogates.
Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general,frongillo2021general}.

@@

To do so, given $u \in U_\epsilon \cap U'_\epsilon \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U_\epsilon,U'_\epsilon$, etc.
The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one permitted value for $\psi(u)$ remains.
This claim follows from a geometric result (Lemma~\ref{lem:thick-intersect}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
When they do intersect, eq.~\eqref{eq:intersection-property-embedding} implies that there exists a permitted choice of link for the intersection of the thickenings.
It is crucial that, by Lemma~\ref{lem:polyhedral-range-gamma}, polyhedral surrogates only have finitely many sets of the form $U = \Gamma(p)$.
Together, these observations yield a single sufficiently small $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
%Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.

@@

Finally, a third proof of Theorem~\ref{thm:poly-ie-implies-consistent} is implicit in \citet[Theorem 8]{ramaswamy2016convex}.
The authors use an entirely different link construction involving the superprediction set of the surrogate loss.
We discuss their result and how it relates to our work in \S~\ref{app:ccdim-construction}.

@@

\paragraph{Polyhedral vs.\ smooth surrogates}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
\footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
\reviewertwo{B}
While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the full conditional label distributions, can improve performance in limited data settings.
We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
  % See references recommended by Peter Bartlett.}
%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
brief pass

\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage{hyperref}

@@

In addition to these changes, we made a few others to address a surprisingly close connection to Ramaswamy and Agarwal (2016, Theorem 8) which was brought to our attention by Dhamma Kimpara, a PhD student at the University of Colorado Boulder.
After translating their definitions to ours, this result essentially states that, for surrogate losses with a finite representative set (the setting of our \S 6), a version of indirect elicitation implies calibration.
As such, they prove a slight generalization of our Theorem 31.
To do so, they provide an alternate link construction to ours.
We therefore felt it important to highlight their work, so we added a new appendix section (\S F) to describe the connection, and added several references to it in context: footnote 1, just before Theorem 17, and just before \S 7.1.

@@

    Thank you; we clarified footnote 2: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''

@@

    We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
    See margin note R2: B.
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

  We have fixed all minor issues.
  We added the definition of a link function to Definition~\ref{def:calibrated}, and emphasized the definition of a calibrated link in Definition~\ref{def:calibrated} as well.
  We added a formal definition of consistency into Appendix~\ref{app:consistency} with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest... let's see how the appendix section turns out} \jessiet{based on first pass of appendix section, might be in favor of adding in to body.}
  We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.

@@

	We thank the reviewer for the suggestion.  Ultimately, however, we feel that such a toy example would not be very illuminating for our particular results.  For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contribution of our paper is in more complex settings.  Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \href{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}{this}. 
	In lieu of a toy example, we feel that the applications in Section~\ref{sec:applications} illustrate the machinery we develop, leaving the evaluation and demonstration of the resulting surrogates (in the proper contexts) to the follow-up works cited there.

>>>>

\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage[draft]{hyperref}
% \usepackage{nohyperref}  % This makes hyperref commands do nothing without errors
\usepackage{url}  % This makes \url work

@@

In addition to these changes, we made a few others to address a surprisingly close connection to Ramaswamy and Agarwal (2016, Theorem 8) which was brought to our attention by Dhamma Kimpara, a PhD student at the University of Colorado Boulder.
After translating their definitions to ours, this result essentially states that, for surrogate losses with a finite representative set (the setting of our \S 6), a version of indirect elicitation implies calibration.
As such, they prove a slight generalization of our Theorem~\ref{thm:poly-ie-implies-consistent}.
To do so, they provide an alternate link construction to ours.
We therefore felt it important to highlight their work, so we added a new appendix section (\S~\ref{app:ccdim-construction}) to describe the connection, and added several references to it in context: footnote 1, just before Theorem~\ref{thm:thickened-separated}, and just before \S 7.1.

@@

    Thank you; we clarified footnote 3: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''

@@

    We added footnote 8 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
    See margin note R2: B.
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

  We have fixed all minor issues.
  We added the definition of a link function to Definition~\ref{def:calibrated}, and emphasized the definition of a calibrated link in Definition~\ref{def:calibrated} as well.
  We added a formal definition of consistency (Definition~\ref{def:consistency}).
  We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.

@@

	We thank the reviewer for the suggestion.  Ultimately, however, we feel that such a toy example would not be very illuminating for our particular results.  For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contribution of our paper is in more complex settings.  Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \url{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}.
	In lieu of a toy example, we feel that the applications in Section~\ref{sec:applications} illustrate the machinery we develop, leaving the evaluation and demonstration of the resulting surrogates (in the proper contexts) to the follow-up works cited there.
